BVP Methods

### 2017-11-21 notes/method_description/bvp_method.tex
writes up FC bvp

>>>>

\section{Extension to Stratified convection and FC equation}
This method is, fortunately, not hard to extend to the fully compressible equations. For
a system whose full energy equation is of the form
$$
\frac{\partial E}{\partial t} + \Div{\bm{F}} = \kappa (\text{IH}),
$$
which is true of both polytropes and internally heated atmospheres, we find that the time
stationary, vertically averaged profile is, once again,
\begin{equation}
\kappa\frac{\partial \angles{T_{1z}}}{\partial z} = 
\frac{\partial}{\partial z}(\angles{\bm{F}_{\text{conv}} - \kappa T_{0z}} - \kappa (IH)
\end{equation}
And, for a properly constructed atmosphere where the initial profile carries the internal
heating, the last two terms of this expression perfectly cancel each other out (at least,
for constant $\kappa$, and for the atmospheres we're worried about right now).  So, with that,
the full set of BVP equations for fully compressible atmospheres is
\begin{equation}
\begin{split}
\frac{\partial T_1}{\partial z} - T_{1z} &= 0 \\
\kappa \frac{\partial T_{1z}}{\partial z} &= \frac{\partial \bm{F}_{\text{conv}}}{\partial z} \\
T_0 \partial_z \rho_1 + T_1 \partial_z \rho_0 + \rho_0 T_{1z} + \rho_1 T_{0z} &= - T_1 \partial_z \rho_1 - \rho_1 T_{1z} \\
\frac{\partial M_1}{\partial z} - \rho_1 &= 0.
\label{eqn:FC_BVP_eqns}
\end{split}
\end{equation}
Here the first two equations are just the energy equation, the third equation is that the
fluctuating components must be in hydrostatic equilibrium ($\grad P = \grad (\rho T) = 
\rho \grad T + T \grad \rho = 0$, and assuming that the background is in hydrostatic equilibrium
such that gravity drops out of the system), and the fourth equation is our mass conservation equation.
This requires four boundary conditions: two thermal ones (fixed flux bot, fixed temp top), and
two mass ones ($M_1 = 0$ at top and bottom).  Once again, by specifying the appropriate profile
for the convective flux, the rest of the atmosphere follows.  This is also nice, because this
formulation should also work with minor tweaks for more complicated forms of $\kappa$.
